Causal.jl:\\A Modeling and Simulation Framework for Causal Models

### 2021-07-03 paper/paper.tex
Added answers2.

>>>>

It is possible for the users to determine the time instants at which the components are sampled. The user-specified sampling time instants can be regularly or irregularly spaced. However, although the sampling time instants are determined by the user, the solvers of the systems take adaptive steps while the systems evolve from one sampling instant to the next. Therefore, the sampling time instants determined by the user do not force the systems to evolve with the specified time intervals but to sample the outputs of the systems at those specified instants.
